---
title: "Lab 00 - Hello IDS!"
author: "NIKOS"
date: "`r Sys.Date()`"
output: html_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

### Exercises 16-17

We set up the data frame. Edit the data below to include information about your team members.

```{r setup-tibble}
team_data <- tibble(
  name = c("Jason","Matias","Sami","Jerry","James"),
  github_username = c("JasonBi615","MatiasLander","Sami-Munawar","JerryL123","James114Jin"), 
  colour = c("pink","blue","green","blue","black"),
  hobby = c("video games","football","drums","video games","ping pong"),
  favourite_number = c(8,5,3,5,7)
  )

team_data
```

### Exercise 18

We now work on visualising our data. 

```{r bar-plot}
p1 <- ggplot(data = team_data, 
             mapping = aes(x = github_username, 
                           y = favourite_number,
                           fill = colour), 
             ) +
   geom_col() +
   scale_fill_identity()
p1
```


*I see columns*

### Exercises 19

Change the text of the plot title and axis labels.

```{r labelled-bar-plot}
p1 + labs(x = "Github username", 
          y = "Favourite number",
          title = "Team's favourite colors")
```

it allows you to label your graph

### Exercise 20

```{r new-bar-plot}
p2 <- ggplot(team_data, aes(x = hobby)) +
  geom_bar()
p2
```

We would get more variation making the graph look more appealing. Also we could add some colors to make it more appealing to the eyes of the consumer
